---
output: github_document
title: "Simple example of a Makefile"
author: "David Gerard"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Introduction

This is a simple example of using a Makefile to organize the pipeline of a basic data analysis.

The files after everything is evaluated are:

- Makefile
- Readme.qmd
- Readme.md
- analysis
    - add_alt_sims.R
    - null_sims.R
    - panal.qmd
- output
    - add_alt_sims.Rout
    - null_sims.Rout
    - panal.html
    - pdat.csv
    - pnull.RDS

These files have the following dependency structure:

```{r dependency-graph, message = FALSE, echo = FALSE}
library(tidyverse)
library(ggdag)
set.seed(15)
dagify("pnull.RDS" ~ "null_sims.R",
       "pdat.csv" ~ "add_alt_sims.R",
       "pdat.csv" ~ "pnull.RDS",
       "panal.html" ~ "panal.qmd",
       "panal.html" ~ "pdat.csv") %>%
  ggdag(layout = "sugiyama",
        text_col = "black",
        node = FALSE) +
  theme_void() +
  xlim(-0.5, 2.5)
```

See the [Makefile](https://github.com/data-science-master/pvalue_sims/blob/master/Makefile) for how to organize this dependency structure.
